\documentstyle{jarticle}
\setlength{\topmargin}{-1cm}
\setlength{\oddsidemargin}{-0cm}
\setlength{\evensidemargin}{-0cm}
\setlength{\textwidth}{440pt}
\setlength{\textheight}{660pt}

\begin{document}

\title{研究業績リスト 2004.1.1}
\author{産業技術総合研究所\\田中 良夫}
\date{}

\maketitle

\section{論文発表}
\begin{thebibliography}{99}
\vspace*{-1cm}

\bibitem{takemiya-04a}
武宮 博, 田中 良夫, 中田 秀基, 関口 智嗣,
``Ninf-G2: 大規模Grid環境での利用に即した高機能，高性能GridRPCシステムの実装と評価'',
情報処理学会論文誌 コンピューティングシステム, 
Vol.~45, No.~SIG~11(ACS~7), pp.~144--159, (Oct. 2004).

\bibitem{nakada-04a}
中田 秀基, 田中 良夫, 松岡 聡, 関口 智嗣,
``耐故障性を重視したRPCシステムNinf-Cの設計と実装'',
情報処理学会論文誌 コンピューティングシステム, 
Vol.~45, No.~SIG~11(ACS~7), pp.~160--170, (Oct. 2004).

\bibitem{watanabe-03a}
渡邊 啓正, 本多 弘樹, 弓場 敏嗣, 田中 良夫, 佐藤 三久,
``Relis-G：計算グリッドのための遠隔ライブラリインストール機構'',
情報処理学会論文誌 コンピューティングシステム, 
Vol.~45, No.~SIG~11(ACS~7), pp.~196--206, (Oct. 2004).

\bibitem{takemiya-04a}
Hiroshi Takemiya, Kazuyuki Shudo, Yoshio Tanaka, and Satoshi Sekiguchi,
``Constructing Grid Applications using Standard Grid Middleware'',
Journal of Grid Computing, Vol.~1, No.~2, pp.~117--131, Kluwer Academic Publishers, (June 2004).

\bibitem{takemiya-03a}
武宮 博, 首藤 一幸, 田中 良夫, 関口 智嗣,
``Grid環境上における気象予報シミュレーションシステムの構築'',
情報処理学会論文誌 コンピューティングシステム, 
Vol.~44, No.~SIG~11(ACS~3), pp.~23--33, (Aug. 2003).

\bibitem{ikegami-03c}
池上 努, 武宮 博, 田中 良夫, 長嶋 雲兵, 関口 智嗣,
``Grid: 広域分散並列環境での高精度分子シミュレーション -- C_{20}分子のレプリカ交換モンテカルロ'',
情報処理学会論文誌 コンピューティングシステム, 
Vol.~44, No.~SIG~11(ACS~3), pp.~14--22, (Aug. 2003).

\bibitem{yoshio-03a}
Y. Tanaka, H. Nakada, S. Sekiguchi, T. Suzumura, and S. Matsuoka,
``Ninf-G: A Reference Implementation of RPC-based Programming Middleware for Grid Computing'',
Journal of Grid Computing, Vol.~1, No.~1, pp.~41--51, Kluwer Academic Publishers, (June 2003).

\bibitem{nakada-02b}
中田 秀基, 齋藤 真幸, 鈴村 豊太郎, 田中 良夫, 松岡 聡, 関口 智嗣,
``Gridポータル構築ツールキットNinf-Portal'',
情報処理学会論文誌 ハイパフォーマンスコンピューティングシステム,
Vol.~43, No.~SIG~6(HPS~5), pp.~172--183, (Sep. 2002).

\bibitem{yoshio-01b}
田中 良夫, 建部 修見, 寺西 慶太, 二方 克昌, 合田 憲人, 関口 智嗣, 原 辰次,
``Network Enabled ServerのWorld-wide Gridにおける性能'',
情報処理学会論文誌 ハイパフォーマンスコンピューティングシステム,
Vol.~42, No.~SIG~9(HPS~3), pp.~64--76, (Aug. 2001).

\bibitem{yoshio-00c}
田中 良夫, 平野 基孝, 佐藤 三久, 中田 秀基, 関口 智嗣,
``ファイアウォールに対応したGlobusによる広域クラスタシステムの構築とその評価'',
情報処理学会論文誌 ハイパフォーマンスコンピューティングシステム,
Vol.~41, No.~SIG~8(HPS~2), pp.~48--59, (Nov. 2000).

\bibitem{itakura-00}
板倉 憲一, 早川 秀利, 近藤 正章, 吉川 茂洋, 朴 泰祐, 佐藤 三久, 田中 良夫,
``メモリバスアクセス率に基づくSMP-PCクラスタの性能評価'',
情報処理学会論文誌 ハイパフォーマンスコンピューティングシステム,
Vol.~41, No.~SIG~5(HPS~1), pp.~70--79, (Aug. 2000).

\bibitem{matu-00}
M. Matsuda, Y. Tanaka, K. Kubota, M. Sato,
``Network interface active message for low overhead communication on SMP PC clusters'',
Future Generation Computer Systems, Vol.~16, No.~5, pp.~493--502, (Mar. 2000).

\bibitem{yoshio-99a}
田中 良夫,  松田 元彦, 久保田 和人, 佐藤 三久,
``COMPaS: Pentium Proを用いたSMPクラスタとその評価'',
情報処理学会論文誌, Vol.~40, No.~5, pp.~2215--2224 (May 1999).

\bibitem{matu-99a}
松田 元彦, 田中 良夫,  久保田 和人, 佐藤 三久,
``SMP クラスタ向けネットワーク・インタフェース AM 通信'',
情報処理学会論文誌, Vol.~40, No.~5, pp.~2225--2234 (May 1999).

\bibitem{dora-97a}
高橋 聡子, 岩井 輝男, 田中 良夫, 前田 敦司, 中西 正和,
``リスト処理とGCのCPU割り当てを動的に決定する並列Lisp'',
情報処理学会論文誌, Vol.~38, No.~5, pp.~1050--1057 (May 1997).

\bibitem{eiko-97a}
田中 詠子, 前田 敦司, 田中 良夫, 中西 正和,
``オブジェクトの生存率の理論的解析に基づいた世代別ガーベッジコレクション'',
情報処理学会論文誌, Vol.~38, No.~4, pp.~835--844 (Apr. 1997).

\bibitem{dora-97b}
高橋 聡子, 岩井 輝男, 前田 敦司, 田中 良夫, 中西 正和,
``並列GCを備えた並列Lispシステムの実装および評価'',
電子情報通信学会論文誌, Vol.~J80-D-1, No.~3, pp.~247--257 (Mar. 1997).

\bibitem{yoshio-96a}
Y. Tanaka, S. Matsui, A. Maeda, and M. Nakanishi,
``Performance Analysis of Parallel Garbage Collection Using Partial
Marking (Partial Marking GCの性能解析)'',
Systems and Computers in Japan, Vol.~27, No.~8, pp.~29--38 (Jul. 1996).

\bibitem{eiko-96a}
田中 詠子, 田中 良夫, 中西 正和,
``Adaptive Garbage Collection -- 実装とその評価 --'',
電子情報通信学会論文誌, Vol.~J79-D-1, No.~5, pp.~253--260 (May 1996).

\bibitem{yoshio-95}
田中 良夫, 松井 祥悟, 前田 敦司, 中西 正和,
``部分印づけを併用した並列GCの提案および効率の解析'',
電子情報通信学会論文誌, Vol.~J78-D-1, No.~12, pp.~926--935 (Dec. 1995).

\bibitem{eiko-95a}
E. Tanaka, Y. Tanaka, and M. Nakanishi,
``Adaptive Garbage Collection and Experiments for
Implementation (Adaptive Garbage Collectionの実装に向けての実験)'',
Systems and Computers in Japan, Vol.~26, No.~12, pp.~8--16 (Nov. 1995).

\bibitem{sho-95a}
松井 祥悟, 田中 良夫, 前田 敦司, 中西 正和,
``相補型ガーベジコレクタ'',
情報処理学会論文誌, Vol.~36, No.~8, pp.~1874--1884 (Aug. 1995).

\bibitem{eiko-94}
田中 詠子, 田中 良夫, 中西 正和,
``Adaptive Garbage Collectionの提案および実験'',
電子情報通信学会論文誌, Vol.~J77-D-1, No.~9, pp.~611--618 (Sep. 1994).
\end{thebibliography}

\clearpage
\section{査読つき会議}
\begin{thebibliography}{99}
\vspace*{-1cm}

\bibitem{yoshio-04a}
Y. Tanaka, H. Takemiya, H. Nakada, and S. Sekiguchi,
``Design, implementation and performance evaluation of GridRPC programming middleware for a large-scale computational Grid'',
Fifth IEEE/ACS International Workshop on Grid Computing, pp.~298--305, 2005.

\bibitem{nakada-04b}
H. Nakada, Y. Tanaka, S. Matsuoka, and S. Sekiguchi,
``The Design and Implementation of a Fault-Tolerant RPC System: Ninf-C'',
HPC Asia 2004, pp.~9--18, 2004.

\bibitem{hirano-04a}
M. Hirano, H. Takemiya, Y. Tanaka, S. Itoh, and S. Sekiguchi,
``Grid PSE Builder: A Framework for Building Web-based Distributed PSE on Grid'',
HPC Asia 2004, pp.~34--41, 2004.

\bibitem{watanabe-04a}
H. Watanabe, H. Honda, T. Yuba, Y. Tanaka, and M. Sato,
``Relis-G: Remote Library Install System for Computational Grids'',
HPC Asia 2004, pp.~54--62, 2004.

\bibitem{takemiya-04a}
武宮 博, 田中 良夫, 中田 秀基, 関口 智嗣,
``Ninf-G2: 大規模Grid環境での利用に即した高機能，高性能GridRPCシステムの実装と評価'',
先進的計算基盤システムシンポジウム SACSIS 2004,
IPSJ Symposium Series Vol.~2004, No.~6, pp.~69--76, 2004.

\bibitem{nakada-04a}
中田 秀基, 田中 良夫, 松岡 聡, 関口 智嗣,
``耐故障性を重視したRPCシステムNinf-Cの設計と実装'',
先進的計算基盤システムシンポジウム SACSIS 2004,
IPSJ Symposium Series Vol.~2004, No.~6, pp.~77--84, 2004.

\bibitem{watanabe-03a}
渡邊 啓正, 本多 弘樹, 弓場 敏嗣, 田中 良夫, 佐藤 三久,
``GridRPCシステムにおけるリモートプログラムシッピング機構'',
インターネットコンファレンス2003, pp.~27--34, 2003.

\bibitem{takemiya-03a}
``Grid環境上における気象予報シミュレーションシステムの構築'',
武宮 博, 首藤 一幸, 田中 良夫, 関口 智嗣,
先進的計算基盤システムシンポジウム SACSIS 2003,
IPSJ Symposium Series Vol.~2003, No.~8, pp.~243--250, 2003.

\bibitem{ikegami-03a}
池上 努, 武宮 博, 田中 良夫, 長嶋 雲兵, 関口 智嗣,
``Grid: 広域分散並列環境での高精度分子シミュレーション -- C_{20}分子のレプリカ交換モンテカルロ'',
先進的計算基盤システムシンポジウム SACSIS 2003,
IPSJ Symposium Series Vol.~2003, No.~8, pp.~251--258, 2003.

\bibitem{nakada-02d}
T. Suzumura, H. Nakada, M. Saito, S. Matsuoka, Y. Tanaka and S. Sekiguchi,
``The Nif Portal: An Automatic Generation Tool for the Grid Portals'',
Java Grande 2002, pp. 1-- 7, 2002.

\bibitem{nakada-02a}
中田 秀基, 齋藤 真幸, 鈴村 豊太郎, 田中 良夫, 松岡 聡, 関口 智嗣,
``Gridポータル構築ツールキットNinf-Portal'',
並列処理シンポジウム JSPP 2002, IPSJ Symposium Series Vol.~2002, No.~8,
pp.~209--216, 2002.

\bibitem{msato-01a}
M. Sato, M. Hirano, Y. Tanaka and S. Sekiguchi,
``OmniRPC: a Grid RPC facility for Cluster and Global Computing in OpenMP'',
Workshop on OpenMP Application and Tools 2001, (2001).

\bibitem{yoshio-00b}
Y. Tanaka, M. Hirano, M. Sato, H. Nakada and S. Sekiguchi,
``Performance Evaluation of a Firewall-compliant Globus-based Wide-area Cluster System'',
9th IEEE International Symposium on High Performance Distributed Computing (HPDC 2000),
pp.~121--128, (2000).

\bibitem{yoshio-99e}
田中 良夫, 平野 基孝, 佐藤 三久, 中田 秀基, 関口 智嗣,
``Globusを用いたグローバルコンピューティング環境の構築とその評価'',
インターネットカンファレンス'99, pp.~97--106 (1999).

\bibitem{yoshio-99d}
Y. Tanaka, M. Hirano, M. Sato, H. Nakada, and S. Sekiguchi,
``Resource Manager for Globus-based Wide-area Cluster Computing'',
1st IEEE International Workshop on Cluster Computing (IWCC'99),
pp.~237--244 (1999).

\bibitem{msato-99}
M. Sato, S. Sato, K. Kusano, and Y. Tanaka,
``Design of OpenMP Compiler for an SMP Cluster'',
The First European Workshop on OpenMP (EWOMP'99), Lund, Sweden, Sep. 1999.

\bibitem{ssato-99}
S. Satoh, K. Kusano, Y. Tanaka, M. Matsuda, and M. Sato,
``Parallelization of Sparse Cholesky Factorization on an SMP
Cluster'',
HPCN'99, pp.~211--220 (Apr. 1999).

\bibitem{matu-99b}
M. Matsuda, Y. Tanaka, K. Kubota and M. Sato,
``Network Interface Active Messages for Low Overhead Communication on
SMP PC Clusters'',
HPCN'99, pp.~764--773 (Apr. 1999). 

\bibitem{sho-99}
松井 祥悟, 田中 良夫, 前田 敦司, 中西 正和,
``並列ガーベジコレクションの実用化技術'',
第40回プログラミング・シンポジウム, 情報処理学会 (Jan. 1999).

\bibitem{ando-98}
M. Ando, Y. Tanaka, K. Kubota, M. Matsuda, Y. Akiyama and M. Sato,
``Performance Characterization of Shared- and Distributed-Memory
Multiprocessors on a Tree Search Problem'',
High Performance Computing Asia '98, pp.~620--629 (Sep. 1998).

\bibitem{yoshio-98a}
Y. Tanaka, M. Matsuda, K. Kubota and M. Sato,
``Performance Improvement by Overlapping Computation and Communication
on SMP Clusters''
International Confrerence on PDPTA'98, Vol.~1, pp.~275--282 (Jul. 1998).

\bibitem{yoshio-98b}
田中 良夫, 松田 元彦, 安藤 誠, 久保田 和人, 佐藤 三久,
``COMPaS: Pentium Proを用いたSMPクラスタとその評価'',
並列処理シンポジウム JSPP'98, IPSJ Symposium Series Vol.~98, No.~7,
pp.~343--350 (Jun. 1998).

\bibitem{yoshio-98c}
Y. Tanaka, M. Matsuda, M. Ando, K. Kazuto and M. Sato,
``COMPaS: A Pentium Pro PC-based SMP Cluster and its Experience''
IPPS Workshop on Personal Computer Based Networks of Workstations,
LNCS No.~1388, pp.~486--497 (Apr. 1998).

\bibitem{kazuto-98}
K. Kubota, Y. Tanaka, M. Matsuda, M. Sato, H. Tezuka, A. Hori, and Y. Ishikawa,
``Communication Performance of Gigabit LAN Workstation Cluster RWC/WSC'',
Parco '97 (Sep. 1997).

\bibitem{yoshio-97a}
Y. Tanaka, K. Kubota, M. Matsuda, M. Sato and S. Sekiguti,
``A Comparison of Data-Parallel Collective Communication Performance
and its Application'',
High Performance Computing Asia '97, pp.~137--144 (Apr. 1997).

\bibitem{eiko-97b}
E. Tanaka, T. Iwai, Y. Tanaka, and M. Nakanishi,
``Visualization of Memory Usage and Garbage Collection'',
Fifteenth IASTED International Conference on Applied Informatics,
No.~259--069, pp.~9--12 (Feb. 1997).

\bibitem{eiko-96b}
E. Tanaka, A. Maeda, Y. Tanaka, and M. Nakanishi,
``Adaptive Garbage Collection based on Theoretical Analysis of
Lifetime of Objects'',
Fourteen IASTED International Conference on Applied Informatics,
No.~243--047, pp.~19--22 (Feb. 1996).

\bibitem{sho-95b}
S. Matsui, Y. Tanaka, A. Maeda, and M. Nakanishi,
``Complementary Garbage Collector'',
International Workshop on Memory Management, LNCS No.~986, pp.~163--177 (Sep. 1995).

\bibitem{eiko-95b}
E. Tanaka, Y. Tanaka, and M. Nakanishi,
``A Theoretical Analysis of Advancement Threshold in Generational
Garbage Collection'',
Thirteenth IASTED International Conference on Applied Informatics,
No.~230--119, pp.~378--381 (Feb. 1995).

\bibitem{ogi-95}
荻原 拓也, 田中 詠子, 岩井 輝男, 田中 良夫, 前田 敦司, 松井 祥悟, 中西 正和,
``GCの視覚化'',
第37回プログラミング・シンポジウム, 情報処理学会 (Jan. 1995).

\bibitem{yoshio-94a}
Y. Tanaka, S. Matsui, A. Maeda, and M. Nakanishi,
``Partial Marking GC (Partial Marking GC)'',
International Conference on Third Joint International Conference on
Vector and Parallel Processing (CONPAR 94 - VAPP VI), LNCS No.~854,
pp.~337--348 (Sep. 1994).

\bibitem{yoshio-93a}
Y. Tanaka, S. Matsui, A. Maeda, and M. Nakanishi,
``Parallel Garbage Collection by Partial Marking and Conditionally
Invoked GC'',
International Conference on Parallel Computing Technologies 93, 
Vol.~2, pp.~397--408 (Sep. 1993).
\end{thebibliography}

\clearpage
\section{研究会等}
\begin{thebibliography}{99}
\vspace*{-1cm}

\bibitem{taimura-04a}
谷村 勇輔, 池上 努, 中田 秀基, 田中 良夫, 関口 智嗣,
``Ninf-G2の性能評価：科学技術計算における事例'',
情報処理学会ハイパフォーマンスコンピューティング研究会，
Vol.~2004, No.~81, pp.~37--42, 2004.

\bibitem{takemiya-04a}
武宮 博, 田中 良夫, 中田 秀基, 関口 智嗣,
``Ninf-G version 2の実装および性能評価'',
情報処理学会ハイパフォーマンスコンピューティング研究会，
Vol.~2004, No.~20, pp.~19--24, 2004.

\bibitem{nakada-03a}
中田 秀基, 田中良夫, 松岡 聡, 関口 智嗣,
``GridRPCを用いたタスクファーミングAPIの試作'',
情報処理学会ハイパフォーマンスコンピューティング研究会,
Vol.~2003, No.~102, pp.~61--66, 2003.

\bibitem{fujita-03a}
藤田 有哉, 田中 良夫, 関口 智嗣,
``Ninf-Gによるグリッド数値計算ライブラリーの構築'',
情報処理学会ハイパフォーマンスコンピューティング研究会,
Vol.~2003, No.~102, pp.~67--72, 2003.

\bibitem{watanabe-03a}
渡邊 啓正, 本多 弘樹, 弓場 敏嗣, 田中 良夫, 佐藤 三久,
``GridRPCシステムにおけるリモートプログラムシッピング機構'',
情報処理学会ハイパフォーマンスコンピューティング研究会,
Vol.~2003, No.~102, pp.~73--78, 2003.

\bibitem{hirano-03a}
平野 基孝, 山本 直孝, 田中 良夫, 伊藤 智, 関口 智嗣,
``GridPSE Builder: グリッドにおける汎用PSE構築ツールの開発'',
情報処理学会ハイパフォーマンスコンピューティング研究会,
Vol.~2003, No.~83, pp.~77--82, 2003.

\bibitem{yoshio-03b}
田中 良夫, 中田 秀基, 朝生 正人, 関口 智嗣,
``Ninf-G2: 大規模環境に即した高機能，高性能GridRPCシステム'',
情報処理学会ハイパフォーマンスコンピューティング研究会,
Vol.~2003, No.~83, pp.~65--70, 2003.

\bibitem{shudo-03b}
首藤 一幸, 大西 丈二, 田中 良夫, 関口 智嗣,
``計算機資源の流通および集約のためのP2Pミドルウェア'',
情報処理学会プログラミング研究会.

\bibitem{ikegami-03b}
池上 努, 武宮 博, 田中 良夫, 長嶋 雲兵, 関口 智嗣,
``Accurate molecular simulation on the Grid''
日本シミュレーション学会.

\bibitem{shudo-03a}
首藤 一幸, 武宮 博, 平野 基孝, 田中 良夫, 関口 智嗣,
``気象予報グリッドポータルの開発'',
情報処理学会ハイパフォーマンスコンピューティング研究会，
Vol.~2003, No.~29, pp.~167-172, 2003.

\bibitem{yoshio-02b}
田中 良夫, 関口 智嗣,
``アジア太平洋グリッドテストベッドの構築'',
情報処理学会ハイパフォーマンスコンピューティング研究会，
%Vol.~2002, No.~51, pp.~55--60, 2002.

\bibitem{hirano-02}
平野 基孝, 佐藤 三久, 田中 良夫, 関口 智嗣,
``OpenGRコンパイラの設計および開発'',
情報処理学会ハイパフォーマンスコンピューティング研究会，
Vol.~2002, No.~51, pp.~55--60, 2002.

\bibitem{shudo-02}
首藤 一幸, 田中 良夫, 小松 弘幸, 松岡 聡, 南里 豪志, 岡村 耕二, 関口 智嗣,
``Access Gridの構築とGrid上での国際会議'',
情報処理学会ハイパフォーマンスコンピューティング研究会，
Vol.~2002, No.~22, pp.~31--36, 2002.

\bibitem{kawato-01}
川戸 正裕, 蒲地 恒彦, 妹尾 義樹, 田中 良夫, 関口 智嗣, 
``Globus ToolkitのNEC SX-4/5への移植および評価'',
情報処理学会ハイパフォーマンスコンピューティング研究会，
Vol.~2001, No.~102, pp.~25--30, 2001.

\bibitem{nakada-01}
中田 秀基, 田中 良夫, 松岡 聡, 関口 智嗣,
``Grid RPCシステムのAPIの提案'',
情報処理学会ハイパフォーマンスコンピューティング研究会，
Vol.~2001, No.~102, pp.~37--42, 2001.

\bibitem{yoshio-01b}
田中 良夫, 中田 秀基, 平野 基孝, 佐藤 三久, 関口 智嗣,
``GlobusによるGrid RPCシステムの実装と評価'',
情報処理学会ハイパフォーマンスコンピューティング研究会，
Vol.~2001, No.~87, pp.~165--170, 2001.

\bibitem{yoshio-00a}
田中 良夫, 平野 基孝, 佐藤 三久, 中田 秀基, 関口 智嗣,
``Firewallに対応したGlobusによる広域クラスタシステムの構築と性能評価'',
情報処理学会ハイパフォーマンスコンピューティング研究会，
Vol.~2000, No.~57, pp.~63--68, 2000.

\bibitem{yoshio-99c}
田中 良夫, 平野 基孝, 佐藤 三久, 中田 秀基, 関口 智嗣,
``globusにおけるResource Managerの試作 -- グローバルコンピューティング
環境の構築に向けて--'',
情報処理学会杯パフォーマンスコンピューティング研究会,
Vol.~99, No.~66, pp.~191--196 (1999).

\bibitem{yoshio-99b}
田中 良夫, 佐藤 三久, 中田 秀基, 関口 智嗣,
``globusを用いたグローバルコンピューティングの性能評価'',
情報処理学会システムソフトウェアとオペレーティングシステム研究会, 
Vol.~99, No.~32, pp.~71--76 (May 1999).

\bibitem{ssato-99}
佐藤 茂久，草野 和寛，田中 良夫，佐藤 三久,
``SMPクラスタ向けOpenMPコンパイラ'',
情報処理学会ハイパフォーマンスコンピューティング研究会，
Vol.~99, No.~66, pp.~ (1999). <br>

\bibitem{msato-98}
佐藤 三久, 田中 良夫, 草野 和寛, 中田 秀基, 関口 智嗣, 長嶋 雲兵, 松岡 聡,
``Ninfによる遠隔計算資源アクセスシステムの構築とグローバルコンピューティ
ングシステムの性能評価'',
情報処理学会ハイパフォーマンスコンピューティング研究会,
Vol.~99, No.~21, pp.~37--42 (Mar. 1999).

\bibitem{ssato-98}
佐藤 茂久, 草野 和寛, 松田 元彦, 田中 良夫, 佐藤 三久
``SMPクラスタにおけるコレスキー分解の並列化'',
情報処理学会ハイパフォーマンスコンピューティング研究会, Vol.~98, No.~73,
pp.~49--54 (Oct. 1998).

\bibitem{yoshio-98d}
田中 良夫, 松田 元彦, 久保田 和人, 佐藤 三久,
``SMPクラスタ上でのリモートメモリ転送を用いた通信と計算のオーバーラップ
による性能改善'',
情報処理学会ハイパフォーマンスコンピューティング研究会, Vol.~98, No.~72,
pp.~121--126 (Aug. 1998).

\bibitem{matu-98a}
松田 元彦, 田中 良夫, 久保田 和人, 手塚 宏史, 石川 裕, 佐藤 三久,
``Windows NT クラスタ上での Myrinet による通信の実現'',
情報処理学会計算機アーキテクチャ研究会, Vol.~98, No.~70,
pp.~145--150 (Aug. 1998).

\bibitem{yoshio-98e}
田中 良夫, 松田 元彦, 佐藤 三久,
``SMPクラスタCOMPaSの性能評価''
情報処理学会ハイパフォーマンスコンピューティング研究会, Vol.~98,
No.~18, pp.~49--54 (Mar. 1998).

\bibitem{yoshio-97b}
田中 良夫, 松田 元彦, 安藤 誠, 久保田 和人, 佐藤 三久,
``SMPクラスタでの共有/分散融合プログラミング'',
情報処理学会ハイパフォーマンスコンピューティング研究会, Vol.~97, No.~75,
pp.~61--66, (Aug. 1997).

\bibitem{matu-97}
松田 元彦, 手塚 宏史, 田中 良夫, 久保田 和人, 安藤 誠, 佐藤 三久,
``SMPクラスタ向けネットワーク・インタフェース上AM通信''
情報処理学会計算機アーキテクチャ研究会, Vol.~97, No.~125, pp.~55--60,
(Aug. 1997).

\bibitem{ando-97}
安藤 誠, 田中 良夫, 久保田 和人, 松田 元彦, 秋山 泰, 佐藤 三久,
``Knapsack問題における共有メモリ型/分散メモリ型並列計算機の性能比較'',
情報処理学会ハイパフォーマンスコンピューティング研究会, Vol.~97, No.~75,
pp.~49--54 (Aug. 1997).

\bibitem{yoshio-97c}
田中 良夫, 田中 詠子, 松井 俊浩,
``並列ごみ集めを備えた並列Lispによる実時間処理能力の評価'',
電子情報通信学会技術研究報告, Vol.~96, No.~597, pp.~31--38 (Mar. 1997).

\bibitem{yoshio-97d}
田中 良夫, 久保田 和人, 佐藤 三久, 関口 智嗣,
``Collective通信を用いたデータ並列プログラムの性能予測''
情報処理学会ハイパフォーマンスコンピューティング研究会, Vol.~97, No.~21,
pp.~69--74, (Mar. 1997).

\bibitem{yoshio-97d}
田中 良夫, 久保田 和人, 佐藤 三久, 関口 智嗣,
``並列アルゴリズムにおけるCollective通信の性能比較''
情報処理学会ハイパフォーマンスコンピューティング研究会, Vol.~96, No.~81,
pp.~19--26, (Aug. 1996).

\bibitem{yoshio-96b}
田中 良夫, 松井 俊浩,
``オブジェクト指向Lisp EusLispへの並列GCの実装'',
情報処理学会プログラミング研究会報告, Vol.~96, No.~33, pp.~1--6 (Mar. 1996).

\bibitem{dora-95}
高橋 聡子, 前田 敦司, 田中 良夫, 岩井 輝男, 中西 正和,
``並列GCを備えた並列Lispシステム''
情報処理学会プログラミング研究会報告, Vol.~4, No.~4, pp.~19--24 (Nov. 1995).

\bibitem{yoshio-94b}
田中 良夫, 松井 祥悟,
``Partial Marking GC'',
情報処理学会全国大会, Vol.~4, pp.~159--160 (Sep. 1994).

\bibitem{yoshio-94c}
田中 良夫, 鈴木 佐江子,
``Visual GC Lisp'',
情報処理学会全国大会, Vol.~4, pp.~161--162 (Sep. 1994).

\bibitem{eiko-94a}
高岡 詠子, 田中 良夫, 中西 正和,
``Adaptive Garbage Collection実現のための実験および実装'',
情報処理学会全国大会, vol.~4, pp.~157--158 (Sep. 1994). 

\bibitem{yoshio-94d}
田中 良夫, 松井 祥悟, 前田 敦司, 中西 正和,
``Partial Marking GC'',
情報処理学会記号処理研究会報告, Vol.~94, No.~49, pp.~17--24
(Jul. 1994).

\bibitem{sho-93}
松井 祥悟, 田中 良夫, 前田 敦司, 高橋 尚子, 中西 正和,
``並列GC LispのUNIX上への実装と評価'',
情報処理学会記号処理研究会報告, Vol.~93, No.~8, pp.~33--40
(Jan. 1993).

\bibitem{yoshio-89}
田中 良夫, 中西 正和,
``LispマシンSYNAPSEを用いた分散処理環境の構築'',
情報処理学会記号処理研究会報告, Vol.~89, No.~24, pp.~1--8 (Mar. 1989).
\end{thebibliography}

\clearpage
\section{著作・刊行物}
\bibitem{shudo-03c}
首藤 一幸, 田中 良夫, 関口 智嗣,
``インタネットの新しい応用の開拓を目指して」小特集2章「計算」応用の開拓 -- 情報のWebから計算・デバイス・ソフトウェアのグリッドへ'',
映像情報メディア学会誌, Vol.~57, No.~12, pp.~1626--1631, (社)映像メディア学会, 2003.

\bibitem{yoshio-02c}
Y. Tanaka, S. Matsui, M. Maeda and  M. Nakanishi,
``Partial Marking GC: Generational Parallel Garbage Collection and its Performance Analysis'',
Advanced LISP Technology, TAYLOR \& FRANCIS, 2002.

\bibitem{matsuo-02}
S. Matsuo, T. Iwai, Y. Tanaka, M. Maeda and  M. Nakanishi,
``A parallel Lisp system which dynamically allocates CPUs to list processing and GC'',
Advanced LISP Technology, TAYLOR \& FRANCIS, 2002.

\bibitem{nakada-02c}
H. Nakada, Y. Tanaka, S. Matsuoka and S. Sekiguchi,
``Ninf-G: a GridRPC system on the Globus toolkit'',
Grid Computing: Making the Global Infrastructure a Reality, John Wiley \& Sons Ltd, 2002.

\end{document}
